On the Functionality of the Multilayer Perceptron

### 2020-11-13 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to thesis paper

\paragraph*{}We outline and detail the steps taken to execute this project from beginning to end.
\textcolor{red}{Does this section need to be included? I'm not sure how to format or organize it}

@@

\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth \textcolor{red}{check this!}. This ensures that all data will have a consistent format when features are extracted. This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).
% ================================================================

>>>>

\paragraph*{}This multi-faceted project includes a great number of steps to ensure it's completion. Here we show a high-level outline of the pieces of this project.

@@

\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth. This ensures that all data will have a consistent format when features are extracted. This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).
% ================================================================
